%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% "ModernCV" CV and Cover Letter
% LaTeX Template
% Version 1.3 (29/10/16)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Xavier Danaux (xdanaux@gmail.com) with modifications by:
% Vel (vel@latextemplates.com)
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
% Important note:
% This template requires the moderncv.cls and .sty files to be in the same 
% directory as this .tex file. These files provide the resume style and themes 
% used for structuring the document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[11pt,a4paper,sans]{moderncv} % Font sizes: 10, 11, or 12; paper sizes: a4paper, letterpaper, a5paper, legalpaper, executivepaper or landscape; font families: sans or roman

\moderncvstyle{casual} % CV theme - options include: 'casual' (default), 'classic', 'oldstyle' and 'banking'
\moderncvcolor{blue} % CV color - options include: 'blue' (default), 'orange', 'green', 'red', 'purple', 'grey' and 'black'

\usepackage{lipsum} % Used for inserting dummy 'Lorem ipsum' text into the template

\usepackage[scale=0.75]{geometry} % Reduce document margins
%\setlength{\hintscolumnwidth}{3cm} % Uncomment to change the width of the dates column
%\setlength{\makecvtitlenamewidth}{10cm} % For the 'classic' style, uncomment to adjust the width of the space allocated to your name

%----------------------------------------------------------------------------------------
%	NAME AND CONTACT INFORMATION SECTION
%----------------------------------------------------------------------------------------

\firstname{Mai} % Your first name
\familyname{Abboud} % Your last name

% All information in this block is optional, comment out any lines you don't need
\title{Curriculum Vitae}
\address{Masakin Barzah}{Damascus, Syria}
\mobile{(+963) 996318787}
\email{ma1991abb@gmail.com}
%\email{mai.abboud@hiast.edu.sy}
%\homepage{staff.org.edu/~jsmith}{staff.org.edu/$\sim$jsmith} % The first argument is the url for the clickable link, the second argument is the url displayed in the template - this allows special characters to be displayed such as the tilde in this example
%\extrainfo{www.linkedin.com/in/mai-abboud-6940761b1}
%\photo[70pt][0.4pt]{pictures/profile} % The first bracket is the picture height, the second is the thickness of the frame around the picture (0pt for no frame)
%\quote{"A witty and playful quotation" - John Smith}

%----------------------------------------------------------------------------------------

\begin{document}

%----------------------------------------------------------------------------------------
%	CURRICULUM VITAE
%----------------------------------------------------------------------------------------

\makecvtitle % Print the CV title

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\section{Education}

\cventry{jan 2020 -- jan 2023}{Master in Robotics}{Higher Institute for Applied Sciences and Technology}{Damascus}{\textit{GPA -- 81.5/100}}{}  % Arguments not required can be left empty
\cventry{2009--2015}{Bachelor of Electronic Systems Engineering}{Higher Institute for  Applied Sciences and Technology}{Damascus}{\textit{GPA -- 73/100}}{}
\cventry{2006--2009}{Secondary School}{Samir Shahin School}{Lattakia}{\textit{GPA --  234/240}}{}

\section{Masters Thesis}

\cvitem{Title}{\emph{Enhancing SwinTrack Algorithm through Temporal Information}}
\cvitem{Supervisors}{Professor Assef Jafar}
\cvitem{Description}{This thesis focuses on the application of deep learning techniques in visual object
	tracking, with a specific emphasis on state-of-the-art (SOTA) trackers utilizing
	transformers. For my research, I selected SwinTrack algorithm as my target for
	improvement, aiming to enhance its performance from an Average Overlap (AO)
	score of 69.6 on the got10k dataset to an AO score of 70.5. Currently, I am in the
	process of writing the associated research paper.}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\section{Experience}

%\subsection{Vocational}

\cventry{February 2021--May 2021}{junior C++ software engineer (Part-time)}{Masah-tech}{Damascus}{}{During my time at Masah-tech, I focused on developing desktop applications using Qt and C++ within the Visual Studio environment. My responsibilities included
	participating in the software development process and contributing to the design and
	implementation of various features.}

%------------------------------------------------

\cventry{October 2018-- April 2019}{Fellow}{UNESCO/Poland Co-sponsored Fellowship  Program in Engineering ed 2018A}{Krakow}{}{As a fellow in the UNESCO/Poland Co-sponsored Fellowship Program, I had the
	opportunity to engage in workshops that centered around the Sustainable Development
	Goals. Additionally, I conducted research in the vision lab at AGH University, specifically
	focusing on motion detection using a moving camera. This experience allowed me to deepen
	my understanding of computer vision techniques and their application in real-world scenarios.}

%------------------------------------------------

%\subsection{Miscellaneous}

\cventry{2015--until now}{Electronic system engineer}{Higher Institute for Applied Sciences and Technology}{Damascus}{}{I have accumulated over five years of experience in the fields of computer vision and
	embedded systems, particularly in DSP (Digital Signal Processors).
	During my tenure, I have successfully completed several noteworthy projects, including:
\begin{itemize}
  \item{Implementation of a real-time Normalized Cross Correlation tracker on DSP Module and
  	FPGA.}
  \item{Supervision of a graduation project in computer vision, implemented on DSP using the C
  	programming language.}
  \item{Development of an image stabilization system utilizing the CRS-03 Gyro, AVR32, and
  	OpenCV.}
  \item{Implementation of digital image stabilization using OpenCV.}
  \item{Test some trackers on Phycore AM57x module, which combines an ARM
  	processor and DSP for computer vision applications.}
\end{itemize}
My experience in these projects has provided me with in-depth knowledge and practical skills
in the areas of computer vision, embedded systems, and programming languages, enabling
me to effectively tackle complex engineering challenges.
}

%\cventry{2009--2010}{Computer Repair Specialist}{Buy More}{Burbank}{}{Worked in the Nerd Herd and helped to solve computer problems. Allowed me to become expert in all forms of martial arts and weaponry.}

%----------------------------------------------------------------------------------------
%	AWARDS SECTION
%----------------------------------------------------------------------------------------

\section{Awards}

\cvitem{2018}{UNESCO/Poland Co-sponsored Fellowship  Program in Engineering ed 2018A fellowship}
%\cvitem{2010}{Top Achiever Award -- Commerce}

%----------------------------------------------------------------------------------------
%	COMPUTER SKILLS SECTION
%----------------------------------------------------------------------------------------

\section{Software and technologies skills}

\cvitem{Basic}{FPGA, Quartus12, \textsc{Verilog}, \textsc{VHDL}, Mathematica, MonoDevelop-linux}
\cvitem{Intermediate}{\textsc{pytorch}, \textsc{numpy},\LaTeX, Linux, google colab, Matlab,\textsc{C++}, Atmega8, Atmega16, AVR32, Atmel Studio, Code Vision}
\cvitem{Advanced}{\textsc{python}, \textsc{OpenCV}, VScode, Code Composer Studio, \textsc{C}, Digital Signal Processors}

%----------------------------------------------------------------------------------------
%	Certificates
%----------------------------------------------------------------------------------------

\section{Certificates}

\cvitem{December 2021}{Neural Networks and Deep Learning from DeepLearning.AI on Coursera}
\cvitem{July 2022}{Improving Deep Neural Networks: Hyperparameter Tuning, Regularization and Optimization on Coursera}
\cvitem{April 2022}{Structuring Machine Learning Projects on Coursera}

%----------------------------------------------------------------------------------------
%	LANGUAGES SECTION
%----------------------------------------------------------------------------------------

\section{Languages}

\cvitemwithcomment{Arabic}{Mothertongue}{}
\cvitemwithcomment{English}{C2 Proficient}{EF SET English Certificate 73/100}
\cvitemwithcomment{French}{Basic}{}

%----------------------------------------------------------------------------------------
%	INTERESTS SECTION
%----------------------------------------------------------------------------------------

\section{Interests}

\renewcommand{\listitemsymbol}{-~} % Changes the symbol used for lists

\cvlistdoubleitem{Hiking}{Reading}
\cvlistdoubleitem{Swimming}{Painting}

%----------------------------------------------------------------------------------------

\end{document}
